---
name: Anthony
surname: Fitch
position: "Electrical Distribution Engineer"
phone: +1 (626) 629-9557
www: ""
email: ""
github: ""
linkedin: "linkedin.com/in/anthony-fitch-58138a149"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Electrical Distribution Engineer with hands-on experience in utility operations, engineering analysis, and grid infrastructure development. Proven ability to lead technical studies, provide cross-departmental support, and improve power system performance. Passionate about innovation, reliability, and professional growth.

# Technical Skills

Software & Tools: Microsoft Excel (Pivot Tables), Microsoft Access, Microsoft Visio, Tableau 10

Engineering Applications: CYME Power Engineering Software

Core Competencies:

Distribution equipment and systems

Technical research and objective analysis

Engineering studies and reporting

Communication and presentation skills

Innovation and technology adoption

Power system analysis

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "Masters of Business Administration", "2023 – 2026", "", "California State Polytechnic University, Pomona",
  "Bachelor of Science in Mechanical Engineering", "2018 – 2021", "", "California State Polytechnic University, Pomona",
  "Liberal Arts, Math & Science", "2013 – 2018", "", "Citrus College, Glendora"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "Dec 2022 – Present", "Southern California Edison",
  list(
    "Provide technical support to internal and external customers as a subject matter expert on the distribution system.",
    "Lead the development, interpretation, and application of engineering standards and designs.",
    "Provided troubleshooting expertise for complex electrical distribution problems."
  ),
  "Electrical Distribution Engineer II",

  "June 2021 – Dec 2022", "Southern California Edison",
  list(
    "Developed numerous 12kV distribution feeder circuits and capital projects for load growth and resiliency.",
    "Updated aged infrastructure and enhanced grid automation and reliability.",
    "Performed short circuit, arc flash, load flow, duct bank heating, and harmonic analysis.",
    "Supported Planning, Troublemen, Operations, Automation, and Customer Support teams."
  ),
  "Electrical Distribution Engineer I",

  "July 2020 – June 2021", "Southern California Edison",
  list(
    "Provided support to distribution engineering team with capital projects and feeder voltage analysis.",
    "Performed short circuit duty analysis and other technical studies."
  ),
  "Distribution Engineering Intern"
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```